```{r}
library(tidyverse)
library(ggplot2)
library(RColorBrewer)
library(foreign)
library(leaflet)
library(magrittr)
library(dplyr)
library(tsibble)
library(lubridate)
library(sf)
```

```{r}
#Import TDOT Traffic Data
traffic <- read.dbf("../data/TrfcHistYR.dbf")
```

```{r}
#Rename columns, convert year column to numeric
colnames(traffic) <- str_to_lower(colnames(traffic))
traffic$year <- as.numeric(as.character(traffic$year))

#Rename columns, filter years, add percent change column, convert year to datetime
traffic <- rename(traffic, long = x, lat = y, daily_traffic = adjavgdly) %>%
  filter(year >= 2009) %>%
  group_by(station_id) %>% 
  mutate(pct_change = (daily_traffic/lead(daily_traffic) - 1) * 100) %>%
  mutate(pct_change = round(pct_change, 2)) %>%
  mutate(year = lubridate::ymd(year, truncated = 2L))

#Remove rows with null or inf Values
traffic$pct_change <- traffic$pct_change %>% replace(is.na(.), 0)
traffic$pct_change[which(!is.finite(traffic$pct_change))] <- 0
```

```{r}
#Remove stations which don't have data for all years. Start by creating a list I will use to filter.
keep_roads <- traffic %>%
  group_by(station_id) %>%
  count(station_id) %>%
  filter(n == 10) %>%
  pull(station_id)
#keep_roads <- remove_roads$station_id
#View(keep_roads)
```

```{r}
#Filter traffic by removing rows with station_id not in keep_roads
traffic <- traffic[traffic$station_id %in% keep_roads, ]
#Find total change in traffic from 2009-2018
traffic <- traffic %>%
  group_by(station_id) %>%
  mutate(ann_growth_rate = ((daily_traffic / lead(daily_traffic, 9L)) ** (1/9) - 1) * 100)
View(traffic)
```

```{r}
#write_csv(traffic, "traffic.csv")
```

######################################################################################################

SKIP FOLLOWING SECTION - DEPRECATED PROJECTION FORMULA (keep for potential future use)
```{r}
# #Create formula for caluclating projected growth. Start with adding a weighting column, and multiplying to create weighted pct.
# traffic <- traffic %>%
#   mutate(weight = year - 2009,
#          weighted_pct_change = weight * pct_change)
```

```{r}
# #Find the projected growth rate using the weighted pct changes
# traffic_proj_rates <- traffic %>%
#   group_by(station_id) %>%
#   summarise(proj_rate = sum(pct_change) / sum(weight) * 100) %>%
#   mutate(year = 2020)
# #View(traffic_proj_rates)
```

```{r}
# #Merge traffic projected rates to main traffic dataframe
# traffic <- traffic %>%
#   bind_rows(traffic_proj_rates) %>%
#   arrange(station_id, desc(year))
# View(traffic)
```

###################################################################################################


FIND WEIGHTED AVERAGE OF TRAFFIC CHANGES PER YEAR
```{r}
traffic_growth <- traffic %>%
  group_by(county, year) %>%
  mutate(traffic_factor = daily_traffic / sum(daily_traffic)) %>% 
  mutate(weighted_traffic = pct_change * traffic_factor) %>%
  summarise(sum(weighted_traffic))
colnames(traffic_growth) <- c("county", "year", "traffic_growth_rate")
traffic_growth <- traffic_growth %>%
  mutate(traffic_growth_rate = round(traffic_growth_rate, 2))
```


######################################################################################################

SKIP FOLLOWING SECTION - DEPRECATED PROJECTION FORMULA (keep for potential future use)

```{r}
# traffic_growth <- traffic %>%
#   group_by(county, year) %>%
#   summarise(sum(daily_traffic) - sum(lead(daily_traffic))) %>% View() 
#     
    
#     traffic_factor = daily_traffic / sum(daily_traffic)) %>% 
#   mutate(weighted_traffic = pct_change * traffic_factor) %>%
#   summarise(sum(weighted_traffic))
# colnames(traffic_growth) <- c("county", "year", "traffic_growth_rate")
# View(traffic_growth)
```

```{r}
# #Create annualized growth rate from 2009-2018
# traffic_growth_nine_yr <- traffic %>%
#   group_by(county, year) %>%
#   summarise(total_daily = sum(daily_traffic)) %>% 
#   arrange(county, desc(year)) %>%
#   mutate(ann_growth_rate = ((total_daily / lead(total_daily, 9L)) ** (1/9) - 1) * 100) %>%
#   filter(year == 2018)
# #View(traffic_growth_nine_yr)
```

```{r}
# #Create annualized growth rate from 2015-2018
# traffic_growth_three_yr <- traffic %>%
#   filter(year >= 2015) %>%
#   group_by(county, year) %>%
#   summarise(total_daily = sum(daily_traffic)) %>% 
#   arrange(county, desc(year)) %>%
#   mutate(ann_growth_rate = ((total_daily / lead(total_daily, 3L)) ** (1/3) - 1) * 100) %>%
#   filter(year == 2018)
# #View(traffic_growth_three_yr)
```

######################################################################################################



MERGE TRAFFIC FORECAST, POPULATION, COMMUTER DATA, AND COUNTY GEOGRAPHY BY COUNTY BY YEAR
```{r}
#import census and county geography data
census_traffic <- read_csv('../data/census_traffic.csv')
counties <- st_read('../data/counties_geo.shp')
```

```{r}
#merge with traffic forecast and counties
census_traffic <- census_traffic %>%
  mutate(year = lubridate::ymd(year, truncated = 2L)) %>%
  inner_join(traffic_growth, by = c("county", "year"))
# counties_data <- counties %>%
#   inner_join(census_traffic, by = "county") %>%
#   st_sf()
# counties_data
counties_data <- inner_join(counties %>% as.data.frame(), census_traffic, by = "county")

#Comment out below line if you want to continue without converting to sf
counties_data %<>% st_sf(sf_column_name = 'geometry')

counties_data
#View(counties_data)
#st_write(counties_data, "counties_data.shp")
#write_csv(counties_data, "counties_data.csv")
```


############################################################################################################

BUILD ANIMATED GGPLOT MAPS (Unsuccessful attempt - Keep for potential future use)
```{r}
tn_map <- counties_data %>%
  filter(year == 2011-01-01) %>%
  ggplot() + geom_sf(data = counties_data, color = "black", aes(fill = population))

#tn_map_animated <- tn_map + transition_manual(frames = date)
  

tn_map
# ggplot(data = counties_data %>% filter(year == 2018)) +
#   geom_sf(color = "black", aes(fill = population))
```

```{r}
# counties_data %>%
#   #mutate(year = as.Date(year)) %>%
#   filter(year == 2018-01-01) %>%
#   ggplot() + geom_sf(data = counties_data, color = "black", aes(fill = population))
# counties_data

counties_data %>%
  filter(year == 2018-01-01) %>%
  ggplot() + geom_sf(data = counties_data, color = "black", aes(fill = population))
```


BEGIN TESTING LEAFLET MAP

```{r}
pal <- colorNumeric(
  palette = "Blues",
  domain = davidson_traffic$pct_change)

davidson_map <- leaflet(davidson_traffic) %>%
  setView(-86.822, 36.134, zoom = 10) %>%
  addTiles() %>%
  addCircleMarkers(
    color = ~pal(pct_change),
    stroke = FALSE, fillOpacity = 0.8,
    lng = ~long,lat = ~lat,
    popup = ~paste0(location,
                    "<br/>Average Daily Traffic: ", adjavgdly,
                    "<br/>Percent Change: ", pct_change))
davidson_map
```



