```{r}
library(shiny)
library(tidyverse)
library(ggplot2)
library(shinydashboard)
library(RColorBrewer)
library(foreign)
library(leaflet)
library(magrittr)
library(dplyr)
library(fpp2)
library(fable)
library(tsibble)
library(lubridate)
library(sf)
library(gganimate)
```

```{r}
traffic <- read.dbf("../data/TrfcHistYR.dbf")
```

```{r}
colnames(traffic) <- str_to_lower(colnames(traffic))
traffic$year <- as.numeric(as.character(traffic$year))
traffic <- rename(traffic, long = x, lat = y, daily_traffic = adjavgdly) %>%
  filter(year >= 2009) %>%
  group_by(station_id) %>% 
  mutate(pct_change = (daily_traffic/lead(daily_traffic) - 1) * 100) %>%
  mutate(year = lubridate::ymd(year, truncated = 2L))
traffic$pct_change <- traffic$pct_change %>% replace(is.na(.), 0)
traffic$pct_change[which(!is.finite(traffic$pct_change))] <- 0
```

```{r}
#Keep roads with all years
keep_roads <- traffic %>%
  group_by(station_id) %>%
  count(station_id) %>%
  filter(n == 10) %>%
  pull(station_id)
#keep_roads <- remove_roads$station_id
#View(keep_roads)
```

```{r}
#Filter traffic by removing rows with station_id not in keep_roads
traffic <- traffic[traffic$station_id %in% keep_roads, ]
#View(traffic)
#expr[expr$cell_type %in% c("hesc", "bj fibroblast"), ]
```

```{r}
#write_csv(traffic, "traffic.csv")
```






SKIP FOLLOWING SECTION - DEPRECATED PROJECTION FORMULA
```{r}
# #Create formula for caluclating projected growth. Start with adding a weighting column, and multiplying to create weighted pct.
# traffic <- traffic %>%
#   mutate(weight = year - 2009,
#          weighted_pct_change = weight * pct_change)
```

```{r}
# #Find the projected growth rate using the weighted pct changes
# traffic_proj_rates <- traffic %>%
#   group_by(station_id) %>%
#   summarise(proj_rate = sum(pct_change) / sum(weight) * 100) %>%
#   mutate(year = 2020)
# #View(traffic_proj_rates)
```

```{r}
# #Merge traffic projected rates to main traffic dataframe
# traffic <- traffic %>%
#   bind_rows(traffic_proj_rates) %>%
#   arrange(station_id, desc(year))
# View(traffic)
```




FIND WEIGHTED AVERAGE OF TRAFFIC CHANGES PER YEAR
```{r}
traffic_growth <- traffic %>%
  group_by(county, year) %>%
  mutate(traffic_factor = daily_traffic / sum(daily_traffic)) %>% 
  mutate(weighted_traffic = pct_change * traffic_factor) %>%
  summarise(sum(weighted_traffic))
colnames(traffic_growth) <- c("county", "year", "traffic_growth_rate")
#View(traffic_growth)
```

```{r}
# traffic_growth <- traffic %>%
#   group_by(county, year) %>%
#   summarise(sum(daily_traffic) - sum(lead(daily_traffic))) %>% View() 
#     
    
#     traffic_factor = daily_traffic / sum(daily_traffic)) %>% 
#   mutate(weighted_traffic = pct_change * traffic_factor) %>%
#   summarise(sum(weighted_traffic))
# colnames(traffic_growth) <- c("county", "year", "traffic_growth_rate")
# View(traffic_growth)
```

```{r}
#Create annualized growth rate from 2009-2018
traffic_growth_nine_yr <- traffic %>%
  group_by(county, year) %>%
  summarise(total_daily = sum(daily_traffic)) %>% 
  arrange(county, desc(year)) %>%
  mutate(ann_growth_rate = ((total_daily / lead(total_daily, 9L)) ** (1/9) - 1) * 100) %>%
  filter(year == 2018)
#View(traffic_growth_nine_yr)
```

```{r}
#Create annualized growth rate from 2015-2018
traffic_growth_three_yr <- traffic %>%
  filter(year >= 2015) %>%
  group_by(county, year) %>%
  summarise(total_daily = sum(daily_traffic)) %>% 
  arrange(county, desc(year)) %>%
  mutate(ann_growth_rate = ((total_daily / lead(total_daily, 3L)) ** (1/3) - 1) * 100) %>%
  filter(year == 2018)
#View(traffic_growth_three_yr)
```


MERGE TRAFFIC FORECAST, POPULATION, COMMUTER DATA, AND COUNTY GEOGRAPHY BY COUNTY BY YEAR
```{r}
#import census and county geography data
census_traffic <- read_csv('../data/census_traffic.csv')
counties <- st_read('../data/counties_geo.shp')
```

```{r}
#merge with traffic forecast and counties
census_traffic <- census_traffic %>%
  mutate(year = lubridate::ymd(year, truncated = 2L)) %>%
  inner_join(traffic_growth, by = c("county", "year"))
# counties_data <- counties %>%
#   inner_join(census_traffic, by = "county") %>%
#   st_sf()
# counties_data
counties_data <- inner_join(counties %>% as.data.frame(), census_traffic, by = "county")
counties_data %<>% st_sf(sf_column_name = 'geometry')
View(counties_data)
counties_data

#st_write(counties_data, "counties_data.shp")
```

p <- part_data %>%
  filter(date == as.Date("2020-03-30")) %>%
  ggplot(aes(x = long, y = lat, group = group)) +
  geom_polygon(aes(fill = confirmed_new), color = "grey70", size = 0.05) + 
  geom_path(data = state_map, colour = "black") +
  coord_map() +
  scale_fill_distiller(trans = "log10", direction = 1, palette = "YlOrRd", na.value = "white", limits = c(1, 1E4), labels = comma)
  
p + 
  transition_manual(frames = date)

BUILD ANIMATED GGPLOT MAPS
```{r}
tn_map <- counties_data %>%
  filter(year == 2011-01-01) %>%
  ggplot() + geom_sf(data = counties_data, color = "black", aes(fill = population, na.value="grey80"))

#tn_map_animated <- tn_map + transition_manual(frames = date)
  

tn_map
# ggplot(data = counties_data %>% filter(year == 2018)) +
#   geom_sf(color = "black", aes(fill = population))
```















TESTING FABLE PACKAGE:
```{r}
#convert to tsibble - test one county for now
forecast_ts <-forecast_df %>%
  mutate(year = lubridate::ymd(year, truncated = 2L)) %>%
  filter(county == "Davidson") %>%
  as_tsibble()
```


```{r}
forecast_ts
```

```{r}
yrs <- c(2001, 2002, 2002, 2002, 2003, 2005)
lubridate::ymd(yrs, truncated = 2L)
```


















BEGIN LEAFLET MAP

```{r}
pal <- colorNumeric(
  palette = "Blues",
  domain = davidson_traffic$pct_change)

davidson_map <- leaflet(davidson_traffic) %>%
  setView(-86.822, 36.134, zoom = 10) %>%
  addTiles() %>%
  addCircleMarkers(
    color = ~pal(pct_change),
    stroke = FALSE, fillOpacity = 0.8,
    lng = ~long,lat = ~lat,
    popup = ~paste0(location,
                    "<br/>Average Daily Traffic: ", adjavgdly,
                    "<br/>Percent Change: ", pct_change))
davidson_map
```




```{r}
#leaflet(options = leafletOptions(minZoom = 0, maxZoom = 18))
```





